---
title: "Bayesian network meta analysis"
author: "Michael Seo and Christopher Schmid"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bayesian network meta analysis}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

We describe how to run Bayesian network meta analysis using this package. First we'll need to load the package.

```{r}
devtools::install_github("MikeJSeo/bnma")
library(bnma)
```

## Preprocessing

It is essential to specify the input data in a correct format. We have chosen to use arm-level data with following input variable names: Outcomes, N or SE, Study, and Treat. Outcomes is the trial results. N is the number of respondents used for binary or multinomial model. SE is the standard error used for normal model. Study is the study indicator for the meta analysis. Lastly, Treat is the treatment indicator for each arm. We generated a fake dataset `fake_data` for illustration.

```{r}
fake_data
```

In order to run network meta analysis in JAGS, we need to relabel study names into to a numeric sequence, i.e. 1 to total number of studies, and relabel the treatment into a numeric sequence according to treatment order specified. If treatment order is not specified, default is to use alphabetical order. In the example below, we set "Placebo" as the baseline treatment.

```{r}
network <- with(fake_data, network.data(Outcomes = Outcomes, Study = Study, Treat = Treat, N = N, response = "binomial", Treat.order = c("Placebo", "Treatment")))
network$Treat.order 
network$Study.order
```

Another important preprocessing step that is done through `network.data` function is to change the arm-level data into study-level data. We store the study-level data of Outcomes as r, Treat as t, N or SE as n or se. We can see how Outcomes changed into a matrix from below. Similarly, if the Outcomes are multinomial, it will change to a 3 dimensional array.

```{r}
network$r
```

## Priors

Priors can be set in the `network.data` function. Most of the parameters for the priors are self-explanatory. For heterogeneity parameters for random effects model, we follow the data format from R package `gemtc`. It should be a list of length 3 where first element should be the distribution (one of dunif, dgamma, dhnorm, dwish) and the next two are the parameters associated with the distribution. Here is an example.

```{r}
network <- with(smoking, network.data(Outcomes = Outcomes, Study = Study, Treat = Treat, N = N, response = "binomial", mean.d = 0.1, hy.prior = list("dhnorm", 0, 5)))
```

## Running the model

Now to run the network, we use the function `network.run`. There are many parameters that can be modified, but the most important is the parameter `n.run` which determines how many final observations the user wants. Gelman-Rubin statitics is checked automatically every `setsize` number of iterations and once the series have converged we store the last half of the sequence. If the number of iteration is less than the number of observations user wanted (`n.runs`), it will sample more to fill the requirement. One of the neat thing about this package is that it checks for convergence automatically and will give an error if the sequence has not converged.
The number that is printed during the running of the model is the Gelman-Rubin statistics.

```{r}
result <- network.run(network, n.run = 30000)
```

## Model Summary

Package include many summary tools that can be used. One of the more useful summary might be the forest plot. Please look over the R package guide for more possible options.

```{r, fig.width = 6, fig.height = 6}
network.forest.plot(result)
```

## Multinomial model

One unique aspect of this network package is that multinomial outcome dataset can be analyzed. Here is an example.

```{r}
network <- with(cardiovascular, network.data(Outcomes, Study, Treat, N, response = "multinomial"))
result <- network.run(network)
summary(result)
```

## Baseline Risk

One important addition to the network package that most packages don't have is the ability to add baseline risk. Here we show how to add common treatment x baseline risk interactions (slopes) and independent baseline. Depending on how we select parameters `baseline` and `baseline.risk`, we can fit a differnt baseline risk model. Please refer to Achana et al (2013) for details.

```{r}
network <- with(certolizumab, network.data(Outcomes = Outcomes, Treat = Treat, Study = Study, N = N, response = "binomial", Treat.order = Treat.order, baseline = "common", baseline.risk = "independent"))
result <- network.run(network)
summary(result)
```

