---
title: "Bayesian network meta analysis"
author: "Michael Seo and Christopher Schmid"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Bayesian network meta analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

We describe how to run Bayesian network meta analysis using this package. First we'll need to load the package.

```{r}
library(bnma)
```

## Preprocessing

It is essential to specify the input data in a correct format. We have chosen to use arm-level data with following input variable names: Outcomes, N or SE, Study, and Treat. Outcomes is the trial results. N is the number of respondents used for binary or multinomial model. SE is the standard error used for normal model. Study is the study indicator for the meta analysis. Lastly, Treat is the treatment indicator for each arm. We generated a fake dataset `fake_data` for illustration.

```{r}
fake_data
```

In order to run network meta analysis in JAGS, we need to relabel study names into to a numeric sequence, i.e. 1 to total number of studies, and relabel the treatment into a numeric sequence according to treatment order specified. If treatment order is not specified, default is to use alphabetical order. In the example below, we set "Placebo" as the baseline treatment.

```{r}
network <- with(fake_data, network.data(Outcomes = Outcomes, Study = Study, Treat = Treat, N = N, response = "binomial", Treat.order = c("Placebo", "Treatment")))
network$Treat.order 
network$Study.order
```

Another important preprocessing step that is done through `network.data` function is to change the arm-level data into study-level data. We store the study-level data of Outcomes as r, Treat as t, N or SE as n or se. We can see how Outcomes changed into a matrix from below. Similarly, if the Outcomes are multinomial, it will be 3 dimensional array.

```{r}
network$r
```






Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
